% !TeX spellcheck = en_US
\begin{enumerate}
	
	\item Solve the system
	$$\begin{pmatrix}
	4 & 0\\
	1 & 2
	\end{pmatrix}\begin{pmatrix}
	x_1 \\ x_2
	\end{pmatrix} = \begin{pmatrix}
	8 \\ 3
	\end{pmatrix}.  $$
	\item Find a reduced QR--decomposition of 
	$$A = \begin{pmatrix}
	4 & 0\\
	0 & -2 \\
	0 & 0
	\end{pmatrix} .$$
	\textit{Hint: Check $\widehat{Q}\widehat{R} = A$.}
	\item Apply Gaussian elimination with partial row pivoting to compute an LU decomposition of 
	$$A = \begin{pmatrix}
	1 & 1\\
	2 & 4
	\end{pmatrix} .$$
	\textit{Hint: Check $PA=LU$.}
	\item Let $A \in \mathbb{R}^{n \times n}$ be invertible and $b \in \mathbb{R}^n$. How many solutions does the system $Ax=b$ have? Give one solution.
	\item Let $A \in \mathbb{R}^{m \times n}$ with $\text{Im}(A)=\mathbb{R}^m$ and $b \in \mathbb{R}^m$. Does the system $Ax=b$ have a solution? Shortly explain your answer.
	\item Let $A = \begin{pmatrix}
	1 & 2\\
	0 & 0
	\end{pmatrix}$ and $b = \begin{pmatrix}
	0\\1
	\end{pmatrix}$. How many solutions does the system $Ax=b$ have? Shortly explain your answer.
	\item ---
	\item Give an example for a matrix $A \in \mathbb{R}^{2 \times 2}$ where the LU-decomposition algorithm
	necessarily needs a permutation step. 
	\item Let $R=(r_{ij})_{ij} \in \mathbb{R}^{n \times n}$ be a (lower or upper) triangular matrix with $r_{nn} = 0$. Is $R$ invertible? Explain your answer.
	\item When is a diagonal matrix invertible? Write down the inverse in this case.
	\item Let $A\in\mathbb{R}^{n \times n}$ and $b \in \mathbb{R}^n$. Also let $\widehat{Q}\widehat{R}$ be a $\underline{\text{reduced}}$ $QR$--decomposition of $A$. What properties do $\widehat{Q}$ and $\widehat{R}$ have? How can we use it to solve the system $Ax = b$?
	\item Consider the system
	$$
	\begin{pmatrix}
	0	&-2				& 1\\
	2	&2				& 0\\
	-2	&-\frac{3}{2}	&0
	\end{pmatrix} x = 
	\begin{pmatrix}
	-5\\
	6\\
	-5
	\end{pmatrix}.
	$$
	\begin{enumerate}
		%	\item Define a matrix $A$ and a vector $b$, so that this system reads as $Ax = b$. 
		\item  Define a matrix $A$ and a vector $b$, so that this system reads as $Ax = b$. Then compute an $LU$-decomposition of $A$ by applying Gaussian elimination with \underline{\textbf{row pivoting}}. Denote the respective matrices $L$, $U$ and $P$, such that $PA = LU$.\\
		(\textit{Hint: Verify the desired properties of the factor matrices and test whether  $PA = LU$ holds.})
		\item Use the result from the $LU$-decomposition to determine an $x$ which solves $Ax=b$.\\
		(\textit{Hint: Test whether $Ax=b$ holds.})
	\end{enumerate}
\end{enumerate}