\begin{enumerate}
	\item Let $A = \begin{pmatrix}1\\1\end{pmatrix} \in \mathbb{R}^{2 \times 1}$. Find a basis for $\text{ker}(A) $ and determine $\text{nullity}(A)$.
	\item Let $Q \in \mathbb{R}^{n \times n}$ be orthogonal and $y \in\mathbb{R}^{n}$. Find a vector $x \in\mathbb{R}^{n}$, so that $y = Qx$.
	\item Let $A \in \mathbb{R}^{m \times n}$ and  $x \in \text{ker}(A^\top)$. Show that $x$ is orthogonal to all columns of $A$.
	\item Let $P\in\mathbb{R}^{n\times n}$ be a projector. Show that $Py = y$ for all $y \in \text{Im}(P)$.
	\item  Let $A \in \mathbb{R}^{n \times n}$ be a positive definite matrix. Show that the diagonal entries are strictly positive, i.e.,  $a_{ii} > 0$ for all $1\leq i\leq n$.\\
	\textit{Hint: Find a vector $x\in\mathbb{R}^{n}$, so that $a_{ii}=x^\top A x$.}
	\item Let  $x=(1,1)^\top$ and $y=(2,0)^\top$. Compute the orthogonal projection $\text{proj}_x(y) $ of $x=(1,1)^\top$ onto $y=(2,0)^\top$. Show that $(y - \text{proj}_x(y))$ and $x$ are orthogonal.
	\item ---
	\item What is the determinant $\det(Q)$ of an orthogonal matrix $Q$?
	\item What does the dimension formula say?
	\item  Show that an invertible matrix $A\in\mathbb{F}^{n \times n}$ has exactly one inverse matrix.
	\item How is a \textit{norm} $L: \mathbb{F}^n \to [0, \infty)$ defined?
	\item How is positive definiteness of a matrix $A\in \mathbb{R}^{n \times n}$ defined? What does this mean for the angle
	between a vector $x \in \mathbb{R}^{n}$ and the vector $z := Ax$?
	\item How is \textit{injectivity} of a function $f\colon X \to Y$ defined?
	\item How is a \textit{scalar product} $P\colon \mathbb{R}^n \times \mathbb{R}^n \mapsto \mathbb{R}$ defined?
	\item Draw the sets $\{x \in \mathbb{R}^{2} \colon \|x\|_p = 1   \}$ for $p=1,2,\infty$.
	\item What is the definition of an orthogonal matrix? What does it mean for the columns of the matrix?
	\item Give two equivalent definitions for the rank of a matrix $A \in \mathbb{R}^{m \times n}$?
	\item  Let $A \in \mathbb{R}^{n \times n}$ be a positive definite matrix. Show that the diagonal entries are strictly positive, i.e.,  $a_{ii} > 0$ for all $1\leq i\leq n$.\\
	\textit{Hint: Find a vector $x\in\mathbb{R}^{n}$, so that $a_{ii}=x^\top A x$.}
	\item Let $A \in  \mathbb{R}^{m \times n}$ be any matrix. Show that $A^TA$ is symmetric and positive semi-definite. 
	\item What is the determinant $\det(Q)$ of an orthogonal matrix $Q$?
	
	
\end{enumerate}
 