\textbf{\normalsize Thin and Fat Full Rank Matrices}

Answer the following questions without using the SVD. Instead, exploit the orthogonality relation between the four fundamental subspaces and the dimension formula.
\begin{enumerate}
	\item  What is the orthogonal complement of $\{0\}$ and  $\Rn$ in $\Rn$, respectively?
	\item Give an example for a matrix $C \in \Rmn$ with $\text{nullity}(C)=0$ (injective).
	\begin{enumerate}
		\item  What do we know about the order relation between $m$ and $n$?  (which one is greater or equal than the other?)
		\item  What do we know about the columns of $C$?		
		\item  Let $b\in \text{im}(C)$. Can we find two distinct $x_1\neq x_2 \in \Rn$ such that $Cx_1=b = Cx_2 $? Explain your answer.
		\item  What do we know about the matrix $C^\top C \in \Rnn$?
	\end{enumerate}
	\item Give an example for a matrix $A\in \Rmn$ with $n > m$ and $\text{rank}(A) < m$.
	\item Give an example for a matrix $R \in \Rmn$ with $\text{rank}(R) =m$ (surjective).
	\begin{enumerate}
		\item What do we know about the order relation between $m$ and $n$?
		\item What do we know about the rows of $R$?
		\item What do we know about the matrix $RR^\top \in \mathbb{R}^{m \times m}$?
		\item Let $b\in \Rm$. Can we find an $x \in \Rn$ such that $Rx=b$? Explain your answer and give an example for your matrix.
	\end{enumerate}
	\item  Give an an example for a matrix $A \in \Rnn$ with $\text{rank}(A) =n$ (invertible).
	\begin{enumerate}
		\item  What do we know about the dimensions of $\ker(A)$, $\ker(A^\top)$ and $\text{im}(A^\top)$?
%		\item  What do we know about the order relation between $m$ and $n$?
		\item  What do we know about the columns and rows of $A$?
        \item Let $b\in \Rn$. Can we find an \textit{unique} $x \in \Rn$ such that $Ax=b$? Explain your answer and give an example for your matrix.
	\end{enumerate}
	\item  \textbf{Bonus*:} Give an an example for a matrix $A \in \Rmn$ with $\text{rank}(A) =\text{rank}(A^\top)$ and $\text{nullity}(A) \neq \text{nullity}(A^\top)$.
\end{enumerate}

 