% !TeX spellcheck = en_US
Give short answers or proofs to the following questions or statements.
\begin{enumerate}
	\item  Let $A \in \mathbb{R}^{n \times n}$ be a positive definite matrix. Show that the diagonal entries are strictly positive, i.e.,  $a_{ii} > 0$ for all $1\leq i\leq n$.\\
	\textit{Hint: Find a vector $x\in\mathbb{R}^{n}$, so that $a_{ii}=x^\top A x$.}
	\item Let $R=(r_{ij})_{ij} \in \mathbb{R}^{n \times n}$ be a (lower or upper) triangular matrix with $r_{11} = 0$. Is $R$ invertible? Explain your answer.	
	\item Let $V$ be a subspace  of $\mathbb{F}^n$. Give the definition of a basis and the dimension of $V$.		
	\item Let $A \in \mathbb{R}^{n \times n}$ be a symmetric and positive definite matrix. What is the relation between its singular values and its eigenvalues?
	\item What is the definition of an orthogonal matrix? What does it mean for the columns of the matrix?
	\item Let $A \in  \mathbb{R}^{m \times n}$ be any matrix. Show that $A^TA$ is symmetric and positive semi-definite.
	\item Assume you are given the singular value decomposition (SVD)
$U \Sigma V^\top = A$ of some matrix $A \in \mathbb{R}^{m \times n}$, where the 
entries on the diagonal of $\Sigma$ are given in a descending order. Use the SVD to write $A$ as a sum of rank--$1$ matrices and for some $k \leq \text{rank}(A)$ denote the best rank-$k$ approximation of $A$ in terms of the Frobenius norm.
	\item Assume you are given the singular value decomposition (SVD) $U \Sigma V^\top = A$ of some matrix $A \in \mathbb{R}^{m \times n}$. Find a singular value decomposition of $A^\top$ and give a basis for $\text{Im}(A)$ and $\text{Im}(A^\top)$.
		\item Assume you are given the singular value decomposition (SVD)
	$U \Sigma V^\top = A$ of some matrix $A \in \mathbb{R}^{m \times n}$. Determine the pseudoinverse $A^+$ of $A$ with the help of the SVD. Explain why $A^+ = A^{-1}$, if $A$ is invertible (\textit{hint:} note that $m=n$ in this case).
	\item Let $A \in \mathbb{R}^{n \times n}$ be symmetric (implying real eigenvalues) and \textit{negative} definite matrix, i.e., $x^\top A x < 0$ for all $x \in \mathbb{R}^{n}\setminus \{0\}$. Show that the eigenvalues of $A$ are strictly negative, i.e., $\lambda < 0 $ for all $\lambda \in \sigma(A) \subset \mathbb{R}$.
	\item Let $A\in\mathbb{R}^{n \times n}$ and $b \in \mathbb{R}^n$. Also let $\widehat{Q}\widehat{R}$ be a $\underline{\text{reduced}}$ $QR$--decomposition of $A$. What properties do $\widehat{Q}$ and $\widehat{R}$ have? How can we use it to solve the system $Ax = b$?	
		\item What does the dimension formula say?
		\item Give an example for a matrix $A \in \mathbb{R}^{2 \times 2}$ where Gaussian elimination with row pivoting performs a row swap in the first step.
		\item What is the determinant $\det(Q)$ of an orthogonal matrix $Q$?
\end{enumerate}