
Answer the following questions.
\begin{enumerate}
	\item How is a \textit{norm} $L: \mathbb{F}^n \to [0, \infty)$ defined?
	%
	\item Assume you are given the singular value decomposition 
	$U \Sigma V^\top = A$ of some matrix $A \in \mathbb{R}^{m \times n}$, where the 
	entries on the diagonal of $\Sigma$ are given in a descending order.
	Denote the best rank-$k$ approximation of $A$ for $k \leq \min\{m,n\}$ and denote the criterion with respect to which this is the best approximation.
	%
	\item Give an example for a matrix $A \in \mathbb{R}^{2 \times 2}$ where the LU-decomposition algorithm
	necessarily needs a permutation step.
	%
	\item Let $\lambda_1 \neq \lambda_2$ be two eigenvalues of a \textit{symmetric} matrix $A \in \mathbb{R}^{n \times n}$, and let 
	$v_1, v_2 \in \mathbb{R}^n$ be corresponding eigenvectors. Proof that $v_1^\top v_2 = 0$.
	%
	\item How is positive definiteness of a matrix $A\in \mathbb{R}^{n \times n}$ defined? What does this mean for the angle
	between a vector $x \in \mathbb{R}^{n}$ and the vector $z := Ax$?
	%
	\item How is \textit{injectivity} of a function $f\colon X \to Y$ defined?
	%
	\item How is a \textit{scalar product} $P\colon \mathbb{R}^n \times \mathbb{R}^n \mapsto \mathbb{R}$ defined?
	%
	%
	\item Assume you are given the singular value decomposition (SVD) $U \Sigma V^\top = A$ of some matrix $A \in \mathbb{R}^{m \times n}$. What is the singular value decomposition of $A^\top$? Give a basis for $\Im(A)$ and $\Im(A^\top)$.
	%
	\item Assume you are given the singular value decomposition (SVD)
	$U \Sigma V^\top = A$ of some matrix $A \in \mathbb{R}^{m \times n}$. Determine the pseudoinverse $A^+$ of $A$ with the help of the SVD. Explain why $A^+ = A^{-1}$, if $A$ is invertible (\textit{hint:} note that $m=n$ in this case).
	%
	\item Let $A \in \mathbb{R}^{n \times n}$ be a matrix. Are the notions of
	injectivity and surjectivity of $A$ equivalent? Give a short justification.
	%
	\item What is the normal equation? Where is it applied?
	%
	\item Give an example of a vector space other than $\mathbb{R}^n$? 
	%
	\item Let $V$ be a vector space over the field $\mathbb{F}$. Give the definition of a basis.
	%
	\item Draw the sets $\{x \in \mathbb{R}^{2} \colon \|x\|_p = 1   \}$ for $p=1,2,\infty$.
	%
	\item What is the purpose of the power method? Write down its iteration instruction.
	%
	\item What is the purpose of the Richardson iteration? Write down its iteration instruction. When does it converge?
	%
	\item Let $R=(r_{ij})_{ij} \in \mathbb{R}^{n \times n}$ be a (lower or upper) triangular matrix with $r_{nn} = 0$. Is $R$ invertible? Explain your answer.
	%
	\item Let $A \in \mathbb{R}^{n \times n}$ be a symmetric matrix. Are its singular values equal to its eigenvalues?
	%
	\item Let  $A \in \mathbb{R}^{m \times n}$ have independent columns. How can we use the $QR$-decomposition of $A$ to solve the least squares problem $
	\min\limits_{x \in \mathbb{R}^n } \| Ax - b \|_2^2.
	$, where $b \in \mathbb{R}^{m}$.
	%
	\item How is the rank of a real matrix $A \in \mathbb{R}^{m \times n}$ defined?
%
	\item What does the dimension formula say?
%
	\item Denote the optimization problem which is related to the principal component analysis.
	%
	\item When is a diagonal matrix invertible? Write down the inverse in this case.
	%
	\item What is the purpose of the $QR$ Algorithm? Write down its iteration instruction.
	%
	\item Consider the iteration $x_{k+1} = Mx_k + b$ for some matrix $M \in \mathbb{R}^{n \times n}$ and vector $b \in \mathbb{R}^n$. Name a sufficient condition for the convergence of this sequence. What is the limit in this case?
	%
	\item What is the definition of an orthogonal matrix? What does it mean for the columns of the matrix?
	%
\end{enumerate}
