% !TeX spellcheck = en_US
\begin{enumerate}
	\item Let $A \in \mathbb{R}^{m \times n}$ and $r:=\text{rank}(A)$. Assume you are given a singular value decomposition 
	$U \Sigma V^\top = A$, where the 
	entries on the diagonal of $\Sigma$ are given in a descending order.
	\begin{enumerate}
			\item Use the SVD to write $A$ as a sum of rank--$1$ matrices.
		\item Let $k \leq r$. Find the best rank-$k$ approximation of $A$, i.e., give a formula for the matrix
		$$A_k = \arg \min_{B \in  \mathbb{R}^{m \times n},~ \text{rank}(B)=k  } \|B-A\|_F.$$ 
		\item Find a singular value decomposition of $A^\top$ and give a basis for $\text{Im}(A)$ and $\text{Im}(A^\top)$.		
		\item Determine the pseudoinverse $A^+$ of $A$ with the help of the SVD. 
		\item Explain why $A^+ = A^{-1}$, if $A$ is invertible.
		\item Assume now that $A$ is symmetric and positive definite. What is the relation between its singular values and its eigenvalues?
	\end{enumerate}
\item ---
\item Consider the matrix
$$A = \begin{pmatrix}
\frac{1}{\sqrt{2}} &-\frac{1}{\sqrt{2}}\\
1&1
\end{pmatrix}.$$
\begin{enumerate}
	\item Derive its singular value decomposition.
	\item Compute $U\Sigma V^T = A$ to check your result.
	\item Write $A$ as a sum of rank-1 matrices.
	\item Is $A$ invertible? Explain your answer.
\end{enumerate}
\item Consider the matrix
$$A = \begin{pmatrix}
\frac{1}{\sqrt{2}} &-\frac{1}{\sqrt{2}}\\
1&1
\end{pmatrix}.$$	
\begin{enumerate}
	\item Derive its singular value decomposition (SVD).\\
	(\textit{Hint:} Compute $U\Sigma V^T$ to check your result.)
	\item Write $A$ as a sum of rank-1 matrices by using the singular values and vectors.
	\item Is $A$ invertible? Use the SVD to answer this question.
\end{enumerate}
\end{enumerate}
 